Supporting information: Tail associations and their impact on extinction risk

### 2019-10-30 MainText.Rmd
added response

<!--FIG : schematic diagram for partial spearman correlation, adapted from BIVAN-->
\begin{figure*}[!h]
\begin{center}
\includegraphics[width=6 cm]{./Results/PartialSpearmanFig.pdf}
\caption{The partial Spearman correlation, $\cor_{l_b,u_b}(u, v)$, within a band can be computed
for any band to describe how the strength of association between $u$ and $v$
varies from one part of the two distributions to another. Diagonal lines 
show two bands, the data in the right/upper band showing
stronger association than those in the left/lower band. This figure was reproduced
largely following Fig. 7 of Ghosh \emph{et al.} (2019).
\label{PartialSpearmanFig}}
\end{center}
\end{figure*}
<!--***DAN: Shyamolina, please change the u and v axis labels on the figure
to x and y, respectively, since we defined those as the ranks in the main text.-->

@@

To calculate extinction risk for a given metapopulation model, given parameters,
and a given choice of tail association,
we simulated the model for $25$ time steps, $10000$ times, using $n=5$ habitat patches.
The equilibrium value of the 
one-patch, deterministic version of the model, $P_e$ (Table \ref{tab_model_summary})
was used as the initial condition in all patches and simulations.
After each time step, if $P_i(t)$ was less than $P_e/10$ then it was set to $0$.
The whole metapopulation was considered to have gone extinct if all patches were $0$
at time step $25$.
<!--***DAN: Shyamolina, please check the above two sentences, is this what you did?
***Shya: I agreed with you upto line 482, the last line "The whole metapopulation was considered to have gone extinct if all patches were $0$ a time step $25$" I could not understand, did you write that conceptually? (then it's ok), 
or you meant I apply that in my code?
***DAN: I wrote it guessing that that was what you did. If that is not what you did,
when we should discuss, preferably as soon as possible, before Friday.
Similarly, the below line explains lines 149-150 of mydispersal.R, I am not fluent in using apply function on two dims at once e.g. c(1,3), you wrote that piece of code, I want to explain you 
on Friday gow I interpret that portion, then I can tell you accurately what I did.
***DAN: I added some comments above the function extrisk in mydispersal.R, after reading those
can you tell me by adding another comment what you did and if what I wrote here was correct?
-->
Extinction risk was the fraction of 10000 metapopulations that went extinct. 
Estimates of extinction risk were plotted together with 95\% confidence intervals
based on a binomial distribution.

>>>>

<!--FIG : schematic diagram for partial spearman correlation, adapted from BIVAN-->
\begin{figure*}[!h]
\begin{center}
\includegraphics[width=6 cm]{./Results/PartialSpearmanFig.pdf}
\caption{The partial Spearman correlation, $\cor_{l_b,u_b}(u, v)$, within a band can be computed
for any band to describe how the strength of association between $u$ and $v$
varies from one part of the two distributions to another. Diagonal lines 
show two bands, the data in the right/upper band showing
stronger association than those in the left/lower band. This figure was reproduced
largely following Fig. 7 of Ghosh \emph{et al.} (2019).
\label{PartialSpearmanFig}}
\end{center}
\end{figure*}
<!--***DAN: Shyamolina, please change the u and v axis labels on the figure
to x and y, respectively, since we defined those as the ranks in the main text.
***Shya: Done.-->

@@

To calculate extinction risk for a given metapopulation model, given parameters,
and a given choice of tail association,
we simulated the model for $25$ time steps, $10000$ times, using $n=5$ habitat patches.
The equilibrium value of the 
one-patch, deterministic version of the model, $P_e$ (Table \ref{tab_model_summary})
was used as the initial condition in all patches and simulations.
After each time step, if $P_i(t)$ was less than $P_e/10$ then it was set to $0$.
The whole metapopulation was considered to have gone extinct if all patches were $0$
at time step $25$.
<!--***DAN: Shyamolina, please check the above two sentences, is this what you did?
***Shya: I agreed with you upto line 482, the last line "The whole metapopulation was considered to have gone extinct if all patches were $0$ a time step $25$" I could not understand, did you write that conceptually? (then it's ok), 
or you meant I apply that in my code?
***DAN: I wrote it guessing that that was what you did. If that is not what you did,
when we should discuss, preferably as soon as possible, before Friday.
Similarly, the below line explains lines 149-150 of mydispersal.R, I am not fluent in using apply function on two dims at once e.g. c(1,3), you wrote that piece of code, I want to explain you 
on Friday gow I interpret that portion, then I can tell you accurately what I did.
***DAN: I added some comments above the function extrisk in mydispersal.R, after reading those
can you tell me by adding another comment what you did and if what I wrote here was correct?
***Shya: Yes, you are correct. I also added commented text in mydispersal.R lines 153-165. Have a look 
to check that you are agreed with me or not.
-->
Extinction risk was the fraction of 10000 metapopulations that went extinct. 
Estimates of extinction risk were plotted together with 95\% confidence intervals
based on a binomial distribution.

### 2019-10-30 SuppMat.Rmd
added response

#========== Schematic fig for partial spearman correlation ==============
pdf("./Results/PartialSpearmanFig.pdf", width=6, height=6)
op<-par(mar=c(6,6,2,2),mgp=c(3,1,0))
plot(mtc_r[1:150,1],mtc_r[1:150,2],type='p',pch=19,col=rgb(0,0,0,0.15),cex=1.5,
     cex.axis=2,cex.lab=2.5,xlab="u",ylab="v")
lines(c(0,0.3),c(0.3,0),type='l')
lines(c(0,0.6),c(0.6,0),type='l')
lines(c(0,1.4),c(1.4,0),type='l')
lines(c(0,1.7),c(1.7,0),type='l')
par(op)
dev.off()
```

>>>>

#========== Schematic fig for partial spearman correlation ==============
pdf("./Results/PartialSpearmanFig.pdf", width=6, height=6)
op<-par(mar=c(6,6,2,2),mgp=c(3,1,0))
plot(mtc_r[1:150,1],mtc_r[1:150,2],type='p',pch=19,col=rgb(0,0,0,0.15),cex=1.5,
     cex.axis=2,cex.lab=2.5,xlab="x",ylab="y")
lines(c(0,0.3),c(0.3,0),type='l')
lines(c(0,0.6),c(0.6,0),type='l')
lines(c(0,1.4),c(1.4,0),type='l')
lines(c(0,1.7),c(1.7,0),type='l')
par(op)
dev.off()
```
